---
title: "September 2024 CTS Viz of the Month"
author: "Kristen Savage"
date: "2024-09-09"
output:
  html_document:
    theme: cerulean
    highlight: tango
    keep_md: TRUE
---

```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Packages used
```{r packages, eval=FALSE}
library(tidyverse)
```

### Description of inputs

* Data
    + A dataframe called "exposures_outcomes" that captures the relevant topic areas for each of your study publications.

* Variables
    + exposure: the risk factor or exposure the publication is focused on. 
    + outcome: the health condition the publication is focused on.
    + title: for tracking purposes your dataframe may already contain the publication title or other variables; those variables will be dropped when we format the data to count outcome-exposure pairs. 

### Visualization code
```{r viz, eval=FALSE}
# format data for viz
exp_out_df <- exposures_outcomes %>% 
  select(outcome, exposure) %>% 
  group_by(outcome, exposure) %>% 
  mutate(count = n()) %>% 
  unique()

# create viz
exp_out_df %>% 
  ggplot(aes(x = exposure,
             y = outcome,
             fill = count))+
  geom_tile(color = "white",
            lwd = 1.5,
            linetype = 1) +
  coord_fixed()+
  scale_fill_distiller(palette = "PuBuGn", trans = "reverse") +
  scale_x_discrete(guide = guide_axis(angle = 90))+
  scale_y_discrete(limits = c("Thyroid Cancer", 
                              "Pancreatic Cancer",
                              "Ovarian Cancer",
                              "Other",
                              "Non-Hodgkin Lymphoma", 
                              "Multiple Myeloma",
                              "Mental Health",
                              "Macular Degeneration", 
                              "Lung Cancer",
                              "Kidney Cancer", 
                              "Head and Neck Cancer",
                              "Endometriosis",
                              "Endometrial Cancer",
                              "Colorectal Cancer",
                              "Cardiovascular Disease",
                              "Breast Cancer", 
                              "Bladder Cancer"))+
  theme_minimal()+
  theme(plot.title = element_text(size=14, color = "#02818a", face='bold', hjust = 0.5),
        axis.title=element_text(face='bold'))+
  guides(fill = guide_colourbar(barwidth = 1,
                                barheight = 9,
                                title = "Count"))+
  labs(title = "Most Common Topics Across CTS Publications",
       x ="Risk Factors", 
       y = "Health Outcomes")

```

##### Files in this folder:

- .png file: image of the viz of the month
- .Rmd file: the code used to create this document
- .html file: a downloadable version of this document