---
title: "February 2024 CTS Viz of the Month"
author: "Kristen Savage"
date: "2024-02-02"
output:
  html_document:
    theme: cerulean
    highlight: tango
    keep_md: TRUE
---

```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Packages used
```{r packages, eval=FALSE}
# list packages here
library(ggplot2)
library(ggtext)
```

### Description of inputs

* Data
    + A data frame called "happy_data" that stores responses to the same question at two points in time (in this case, questionnaire 1 and questionnaire 6). Each row captures a survey response option and the proportion of respondents that selected that answer at two different points in time.

* Variables
    + answer:the answer choices as text
    + q1: the % (as a number) of participants who selected each answer choice at questionnaire 1
    + q6: the % (as a number) of participants who selected each answer choice at questionnaire 6

### Visualization code
```{r viz, eval=FALSE}
happy_data %>% 
  ggplot() +
  geom_segment( aes(x=answer, xend=answer, y=q1, yend=q6), color= "#BFDBF7") +
  geom_point( aes(x=answer, y=q1), color="#DC9E82", size=12 ) +
  geom_point( aes(x=answer, y=q6), color="#1F7A8C", size=12 ) +
  coord_flip()+
  theme_minimal() +
  theme(plot.title = element_markdown(face = "bold", size = 13, vjust = -2),
        plot.subtitle = element_text(face = "italic", vjust = -3),
        axis.text.x = element_blank(),
        axis.text.y = element_text(face = "bold", size = 10, color = "#030027"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank())+
  ggtitle("How happy were participants at <br><span style = 'color: #DC9E82;'>study enrollment (1995-1996)</span> vs. at <span style = 'color: #1F7A8C'>questionnaire 6 (2017-2019)</span>?",
          subtitle = "All in all, how happy are you these days?")+
    xlab("")+
  ylab("")+
  annotate(geom="text", x = 0.8, y=55, label="% of respondents",
              color="black", fontface = "italic")+
  annotate(geom="text", x="very happy", y=49, label="49",
              color="white", fontface = "bold")+
  annotate(geom="text", x="very happy", y=59, label="59",
              color="white", fontface = "bold")+
  annotate(geom="text", x="somewhat happy", y=36, label="36",
              color="white", fontface = "bold")+
  annotate(geom="text", x="somewhat happy", y=33, label="33",
              color="white", fontface = "bold")+
  annotate(geom="text", x="not very happy", y=4.7, label="4",
              color="white", fontface = "bold")+
  annotate(geom="text", x="not very happy", y=2, label="2",
              color="white", fontface = "bold") 
```

##### Files in this folder:

- .png file: image of the viz of the month
- .Rmd file: the code used to create this document
- .html file: a downloadable version of this document