---
title: "October 2024 CTS Viz of the Month"
author: "Emma Spielfogel"
date: "2024-10-10"
output:
  html_document:
    theme: cerulean
    highlight: tango
    keep_md: TRUE
---

```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Packages used
```{r packages, eval=FALSE}
library(tidyverse)
library(ggvenn)
library(ggtext)
```

### Description of inputs

* Data
    + A dataframe called "venndata" that includes modifiable risk factors as boolean (True/False) values for each participant

* Variables
    + no_exercise: a variable containing 1 or TRUE for each participant who reported no exercise and 0 or FALSE for those who reported any exercise
    + ever_smoker: a variable containing 1 or TRUE for each participant who reported ever smoking and 0 or FALSE for those who reported never smoking

### Visualization code
```{r viz, eval=FALSE}

# change variables which were in 0=No, 1=Yes format into boolean (T/F) format
venndata <- data_in %>%
  select(ever_smoker,no_exercise) %>% 
  mutate(across(c(ever_smoker,no_exercise), as.logical))

# set names for circles
Names <- c("No Exercise","Ever Smoker")

# create scaled venn diagram
venndiagram <- venndata %>% 
  ggplot() +
  theme_void(base_size = 12, base_family="Palatino") +
  geom_venn(aes(A = no_exercise, B = ever_smoker),
            set_names = Names,
            fill_color = c("#0073C2FF", "#EFC000FF"),
            stroke_size = 0.5,
            set_name_color = c("#0073C2FF", "#EFC000FF"),
            show_outside = "always",
            auto_scale = TRUE) +
  annotate("text",x=-.8,y =-1.9,
           label = "participants in neither \nof these groups",
           family = "Arial",
           size = 3.5) +
  coord_fixed() +
  labs(title = "What is the overlap of modifiable risk factors in the CTS?",
       caption = "This chart includes participants who responded to the 
       exercise and smoking habits questions on the baseline survey. 
      \nDefinitions: no exercise: 0 hours/week; 
       ever smoker: current or former smoker") +
  theme(plot.caption = element_markdown(size=10, color="gray30",hjust= 0.45),
        plot.title = element_text(size = 20, color = "gray30", hjust = 0.5),
        plot.margin = unit(c(.5,.1,.5,.1), 'cm'))
```

##### Files in this folder:

- .png file: image of the viz of the month
- .Rmd file: the code used to create this document
- .html file: a downloadable version of this document