---
title: "July 2023 CTS Viz of the Month"
author: "Emma Spielfogel"
date: "2023-07-17"
output:
  html_document:
    theme: cerulean
    highlight: tango
    keep_md: TRUE
---

```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Packages used
```{r packages, eval=FALSE}
library(tidyverse)
library(waffle)
library(hrbrthemes)
```

### Description of inputs

* Data
    + A dataframe called "teachtype" where each unique combination of employment type, years  & count of participants is a row

* Variables
    + TeacherType: a categorical variable describing the types of employment in schools
    + SchoolYears: an ordinal variable representing the 5 groupings of years participants were employed in schools. SchoolYears_Label is used to apply descriptive labels to the axis.
    + Values: the number of participants in each TeacherType and SchoolYears category. This variable is divided by 100 in the ggplot code such that each circle represents 100 participants.

* Inspiration & more about the waffle package:
    + https://rud.is/rpubs/building-waffle-charts.html


### Visualization code
```{r viz, eval=FALSE}
teachtype %>% 
  ggplot(aes(fill = TeacherType,
             Values = N/100)) +
  geom_waffle(color = "white",
              size = .2,
              n_rows = 10,
              flip = TRUE,
              na.rm=FALSE, 
              radius = unit(4.7, "pt")) +
  facet_wrap(~(fct_reorder(SchoolYears_Label,SchoolYears)),
             nrow = 1,
             strip.position = "bottom") +
  scale_x_discrete() +
  scale_y_continuous(labels = function(x) x * 1000,
                     expand = c(0,0)) +
  ggthemes::scale_fill_few() +
  coord_equal() +
  labs(
    title = "California Teachers Study Employment Profile",
    subtitle = "at study enrollment",
    x = "Years Working in CA School System",
    y = "Number of Participants\n",
    fill = "Employment") +
  theme_minimal(base_family = "Times New Roman") +
  theme(legend.position = "right",
        panel.grid = element_blank(),
        axis.ticks.y = element_line()) +
  guides(fill = guide_legend(reverse = TRUE))
```

##### Files in this folder:

- .png file: image of the viz of the month
- .Rmd file: the code used to create this document
- .html file: a downloadable version of this document