---
title: "April 2024 CTS Viz of the Month"
author: "Emma Spielfogel"
date: "2024-04-04"
output:
  html_document:
    theme: cerulean
    highlight: tango
    keep_md: TRUE
---

```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Packages used
```{r packages, eval=FALSE}
library(tidyverse)
```

### Description of inputs

* Data
    + A long dataframe called "retirement_at_questionnaire" where each row contains a participant, the follow-up questionnaire name, their age at that questionnaire, and their retirement status as reported on that questionnaire. Each participant has as many rows in the data as relevant questionnaires they completed.
    
* Variables
    + Retirement_Status: the retirement status of the participant
    + Age_at_Questionnaire: the age of the participant at the time of the questionnaire which asked about retirement
    + Questionnaire: the name of the follow-up questionnaire (i.e. Q3, Q4, Q5) 

### Visualization code
```{r viz, eval=FALSE}
retirement_at_questionnaire %>%
  ggplot(aes(x=Retirement_Status,
             y=Age_at_Questionnaire)) +
  geom_violin(fill="darkgreen",
              color = "darkgreen",
              alpha = 0.5) +
  facet_grid(~Questionnaire) +
  labs(title = "Retirement status by age at CTS questionnaire",
       x = "\nRetirement Status",
       y = "Age at Questionnaire\n") +
  theme_bw() +
  theme(text = element_text(family = "Palatino", size = 16),
        axis.text.y = element_text(size = 16),
        strip.background = element_rect(fill="#ad95b5"),
        plot.background = element_rect(fill = "#adbecf"))
```

##### Files in this folder:

- .png file: image of the viz of the month
- .Rmd file: the code used to create this document
- .html file: a downloadable version of this document