---
title: "CTS population maps"
author: "Danielle Medgyesi"
date: "02/07/2023"
output:
  html_document: default
  pdf_document: default
---

### Packages used

```{r setup, warning=FALSE, message=FALSE}

library(tidyverse)
library(ggplot2)
library(sf)
library(viridis)
library(Hmisc)

```


### Description of inputs

* Data
  + CTS dataframe of County FIPS codes for 124,685 participants living in California at baseline. *Must request access to the data, which can be stored and viewed only in the CTS Data Commons.*
  + Shapefile of California county boundaries, Census 1990. *See subfolder "county_boundaries".*
  
* Variables
  + CensusCountyFips: county FIP code of participant's address at baseline
  + N: Number of participants living in each county 



### Count the number of participants in each county 

```{r}

#Address data requires special permission 
#Only to be viewed and analyzed in CTS secured data commons
#baseline_county<-  read.csv() 


baseline_county<- baseline_county %>% 
                      group_by(CensusCountyFips) %>% 
                      summarise(N=n(), Percent=round(100*(n()/nrow(.)),2))


```


### Merge with shapefile of California county boundaries 

```{r}


county<- st_read(dsn="county_boundaries", quiet=TRUE)


county_pop_sf<- county  %>% left_join(baseline_county, by=c("CO"="CensusCountyFips"))


```

### Visualization code 

```{r fig.width=5, fig.height=5}

# number of participants categorized 
county_pop_sf<- county_pop_sf %>% 
  mutate(N_cat= cut2(N, cuts = c(100,300,500, 700, 1500, 3000, 7000, 10000)))

ggplot(county_pop_sf)+geom_sf(mapping=aes(fill=N_cat), color=NA)+ 
  scale_fill_viridis(discrete = TRUE, option = "plasma", direction = -1, 
                     labels=c("<100", "100-<300", "300-<500", "500-<700", "700-<1500",
                              "1500-<3000", "3000-<7000", ">10000"), 
                     name="Participants")+
  theme(axis.text = element_blank(), 
        axis.title =element_blank(),
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        axis.ticks=element_blank(), 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        panel.background = element_blank(), 
        plot.caption = element_text(hjust = 0), 
        legend.position = c(0.9,0.67), 
        legend.background = element_blank())+
  labs(title="CTS county population at baseline (1995-1996)", 
       caption = "Total participants= 124,685\n\nDesign: Danielle Medgyesi | dm3688@cumc.columbia.edu")

ggsave("CTS_county_pop_map_viz.png",width = 5, height = 5)


```
