---
title: "June 2024 CTS Viz of the Month"
author: "Emma Spielfogel"
date: "2024-06-06"
output:
  html_document:
    theme: cerulean
    highlight: tango
    keep_md: TRUE
---

```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Packages used
```{r packages, eval=FALSE}
library(tidyverse)
library(ggtext)
```

### Description of inputs

* Data
    + A dataframe called q6_sleep where each row is a survey question with a yes/no answer, containing a column for the rate of "yes" responses to each survey question

* Variables
    + sleep_problem: a column where each row corresponds to a yes/no survey question, in this case about sleep-related problems
    + yes_rate: the rate of "yes" responses to each sleep-related problems survey question

### Visualization code
```{r viz, eval=FALSE}
# prepare data for visualization
q6_code <- q6_sleep %>% 
  mutate(
    no_rate = 1 - yes_rate,
    sleep_problem = fct_reorder(sleep_problem, yes_rate)
  ) %>%
  pivot_longer(
    cols = -sleep_problem,
    names_to = 'answer',
    names_pattern = '(.+)_rate',
    values_to = 'percentage'
  )

# create chart
q6_code %>% 
  ggplot(aes(y = sleep_problem, x = percentage, fill = answer)) +
  geom_col(show.legend = FALSE) +
  theme_minimal(base_size = 18, base_family = 'Tahoma') +
  theme(
    plot.title.position = 'plot',
    panel.grid.minor = element_blank(),
    panel.grid.major.y = element_blank(),
    plot.caption = element_markdown(size=10, color="gray30",hjust=0)
  ) +
  labs(
    x = element_blank(), 
    y = element_blank(),
    title = 'Percent of participants who said they:',
    caption = "Sleep questions from the 6th CTS questionnaire"
  ) +
  scale_x_continuous(labels = scales::label_percent()) +
  scale_fill_manual(
    values = c('yes' = '#5FB6C7'),
    na.value = 'grey95'
  )
```

##### Files in this folder:

- .png file: image of the viz of the month
- .Rmd file: the code used to create this document
- .html file: a downloadable version of this document