---
title: "October 2023 CTS Viz of the Month"
author: "Emma Spielfogel"
date: "2023-10-02"
output:
  html_document:
    theme: cerulean
    highlight: tango
    keep_md: TRUE
---

```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Packages used
```{r packages, eval=FALSE}
library(scales)
library(tidyverse)
library(janitor)
library(ggthemes)
library(patchwork)
```

### Description of inputs

* Data
    + A dataframe called "cancer_data" where each row is the unique combination of cancer type, year of diagnosis and count of cases

* Variables
    + cancer_site: the cancer type
    + year_of_diagnosis: the year of cancer diagnosis
    + n: the sum of cancer diagnoses in that year for a particular cancer site

### Visualization code
```{r viz, eval=FALSE}
# Data preparation: create cumulative yearly counts by site
counts <- cancer_data %>%
  group_by(cancer_site,year_of_diagnosis) %>% 
  summarise(frequency = sum(n)) %>%
  mutate(cumulative_sum=cumsum(frequency)) %>% 
  ungroup()

# Data preparation: create total yearly counts for use as a text label
frequency_totals <- cancer_data %>% 
  group_by(year_of_diagnosis) %>% 
  summarise(year_total = sum(n)) %>% 
  ungroup()

# Data preparation: get the total cumulative count of cancers for use as a text label
total_cancers <- counts %>% 
  summarise(total_cumulative = sum(frequency))

# Visualization code: cancer frequencies
freq_chart <- counts %>% 
  ggplot(aes(x=year_of_diagnosis)) +
  geom_bar(aes(y=frequency, fill=reorder(cancer_site,frequency)), stat="identity") +
  scale_fill_tableau(palette = "Tableau 20") +
  geom_text(data=frequency_totals,aes(y=year_total, label = year_total),
            color = "black",
            family = "serif",
            vjust = -1,
            size = 3.5) +
  scale_x_continuous(breaks = c(1995, 2000,2005, 2010, 2015, 2020)) +
  scale_y_continuous(limits = c(0, 1575)) +
  labs(title = "Cancers in the CTS Over Time by Cancer Type",
       subtitle = "Annual counts and cumulative total",
       x = "",
       y = "Number of Cancers\n",
       fill = "Cancer type") +
  theme_tufte(base_size = 16) +
  theme(legend.position="top")

# Visualization code: cumulative frequencies
cumulative_chart <- counts %>% 
  ggplot() +
  geom_bar(aes(x=year_of_diagnosis,y=cumulative_sum, fill=reorder(cancer_site,cumulative_sum)), stat="identity",
           show.legend = FALSE) +
  scale_fill_tableau(palette = "Tableau 20") +
  geom_text(data=total_cum,aes(x=2020,y=total_cumulative, label = paste0(comma(total_cumulative),
                                                                         "\ntotal cancers")),
            color = "black",
            family = "serif",
            vjust = -.2,
            size = 4.2) +
  scale_x_continuous(breaks = c(1995, 2000,2005, 2010, 2015, 2020)) +
  scale_y_continuous(limits = c(0, 40000)) +
  labs(title = "",
       x = "\nYear of Diagnosis",
       y = "Cumulative Number of Cancers\n",
       fill = "Cancer site")+
  theme_tufte(base_size = 16)

# Create a layout for putting both charts together
layout <- "
AAAA
AAAA
AAAA
BBBB
BBBB
BBBB
"

# Combine the two charts
output <- freq_chart + cumulative_chart  +
  plot_layout(design=layout)
```

##### Files in this folder:

- .png file: image of the viz of the month
- .Rmd file: the code used to create this document
- .html file: a downloadable version of this document