---
title: "April 2023 CTS Viz of the Month"
author: "Emma Spielfogel"
date: "2023-04-18"
output:
  html_document:
    theme: cerulean
    highlight: tango
    keep_md: TRUE
---

```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Packages used
```{r packages, eval=FALSE}
library(tidyverse)
library(rnaturalearth)
library(sf)
library(ggsflabel)
```

### Description of inputs

* Data
    + A data frame called "cts_researcher_universities" containing the latitude and longitude of the researcher institutions and institution names
    + A data frame called "usa" containing coordinate data for a background map

* Variables
    + geometry: the geospatial location of each institution, ascertained from the latitude and longitude
    + institution: the name of the research institution as it should appear on the label

### Visualization code
```{r viz, eval=FALSE}

# Code to get coordinate data for background map of continental USA
usa <- ne_states(country = "united states of america", returnclass = "sf") %>% 
  filter(! name %in% c("Alaska","Hawaii"))

# Code to get institution geometry from latitude and longitude
institutions <- cts_researcher_universities %>% 
  st_as_sf(coords=c("longitude","latitude"), crs=4326) %>% 
  st_transform() %>%
  group_by(institution) %>% 
  summarize(count = n())

# Visualization code
ggplot() +
  geom_sf(data = usa,
          fill = "lightgrey",
          color = "grey",
          alpha = 0.3) +
  geom_sf(data = institutions, 
          aes(geometry = geometry,
              color = "#009ED8", fill = "#009ED8"),
              shape=21,
              size = 2,
              color="white",
              fill="#009ED8",
              show.legend=FALSE) +
  geom_sf_label_repel(data = institutions,
               aes(label = institution),
               max.overlaps = 40,
               color = "#006990",
               segment.color="#009ED8",
               size = 1.8,
               min.segment.length=0) +
  theme_void() +
  labs(title = "CTS Researcher Institutions in the US",
       y = "",
       x = "")
```

##### Files in this folder:

- .png file: image of the viz of the month
- .Rmd file: the code used to create this document
- .html file: a downloadable version of this document