---
title: "May 2024 CTS Viz of the Month"
author: "Kristen Savage"
date: "2024-05-05"
output:
  html_document:
    theme: cerulean
    highlight: tango
    keep_md: TRUE
---

```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Packages used
```{r packages, eval=FALSE}
library(tidyverse)
library(ggplot2)
```

### Description of inputs

* Data
    + A dataframe called family_history where each cell is a unique count of the cases for that specific health condition among that family relation

* Variables
    + condition: the list of conditions in your dataset
    + mom: a column that captures the count of maternal cases reported for each respective health condition
    + dad: a column that captures the count of paternal cases reported for each respective health condition
    + grandma: a column that captures the count of cases reported for each respective health condition among participants' material and/or paternal grandma
    + grandpa: a column that captures the count of cases reported for each respective health condition among participants' material and/or paternal grandpa
    + sister: a column that captures the count of sibling (sister-only) cases reported for each respective health condition
    + brother: a column that captures the count of sibling (brother-only) cases reported for each respective health condition
    + daughter: a column that captures the count of cases reported for each respective health condition among participants' daughters
    + son: a column that captures the count of cases reported for each respective health condition among participants' sons

### Visualization code
```{r viz, eval=FALSE}
# pivot data for visualization purposes
family_history <- family_history %>% 
  pivot_longer(cols = !condition, names_to = "relation", values_to = "value") 

# create scatterplot
family_history %>% 
ggplot(aes(x = relation, 
           y = forcats::fct_rev(factor(condition)), 
           fill = value, 
           size = value)) +
  geom_point(shape = 21, stroke = 0, stat = 'identity') +
  scale_x_discrete(limit= c('mom', 'dad', 'grandma', 'grandpa', 'sister', 
                            'brother', 'daughter', 'son'))+
  scale_radius(range = c(1, 10)) +
  scale_fill_gradient(low = "orange", high = "blue", 
                      breaks = c(0, 20000, 42000),
                      labels = c("0", "20K", "40K"),
                      limits = c(0, 42000)) +
  theme_minimal() +
  theme(legend.position = "bottom", 
        panel.grid.major = element_blank(),
        legend.text = element_text(size = 8),
        legend.title = element_text(size = 8)) +
  guides(size = guide_legend(override.aes = list(fill = NA, color = "black", 
                                                 stroke = .25), 
                             label.position = "bottom",
                             title.position = "bottom", 
                             order = 1),
         fill = guide_colorbar(ticks.colour = NA, 
                               label.position = "bottom",
                               title.position = "bottom", 
                               order = 2)) +
  labs(title = "Family Health Conditions Reported at Baseline",
       size = "Number of Participants", 
       fill = NULL, 
       x = NULL, 
       y = NULL) 
```

##### Files in this folder:

- .png file: image of the viz of the month
- .Rmd file: the code used to create this document
- .html file: a downloadable version of this document