---
title: "March 2024 CTS Viz of the Month"
author: "Kristen Savage"
date: "2024-03-01"
output:
  html_document:
    theme: cerulean
    highlight: tango
    keep_md: TRUE
---

```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Packages used
```{r packages, eval=FALSE}
library(treemap)
library(tidyverse)
```

### Description of inputs

* Data
    + A dataframe called "ses_data" that captures the percent of urban and rural participants that belong to each socioeconomic category (or quartile) as well as the color for each socioeconomic category
    
* Variables
    + group: urban or rural status at cancer diagnosis as text
    + ses_cat: a socioeconomic quartile variable, where 1 is the lowest quartile and 4 is the highest quartile
    + value: a numeric value that stores the percent of participants that fall into each group and ses_cat combination (i.e. the percent of rural participants in quartile 1)
    + color: the color you want for each ses_cat in your treemap 

### Visualization code
```{r viz, eval=FALSE}
ses_data %>% 
   treemap(index = c("group","ses_cat"),
           vSize ="value",
           vColor = "color",
           type ="color",
           title = "Socioeconomic Quartiles of Rural and Urban Participants with Cancer",
           fontsize.title = 16,
           fontsize.labels = c(14,12),
           border.col = c("white","white"),
           border.lwds = c(8,2),
           bg.labels= 0,
           align.labels=list(
              c("left", "top"), 
              c("right", "bottom")),
           inflate.labels = F,
           algorithm="pivotSize",
           sortID="ses_cat"
   )
```

##### Files in this folder:

- .png file: image of the viz of the month
- .Rmd file: the code used to create this document
- .html file: a downloadable version of this document